\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2022-08-16 main.tex
committing phase two

Traditional approaches of evolutionary game theory assume that individuals meet
each other at random in an infinitely large well-mixed population, an example of
such an approach is the replicator dynamics. The replicator dynamics describes
how the abundance of strategic types in a population changes based on their
fitness. In this deterministic formulation, individuals with higher fitness
increase in abundance and ultimately, the system reaches a stable fixed point in
which the population may consist either of a single type or of a mixture of
different types. The works of~\cite{nowak2004emergence, taylor2004evolutionary,
imhof2005evolutionary, imhof2006evolutionary, traulsen2007pairwise} have shown
that constraining the population to be finite can lead to fundamental changes
due to stochastic effects. Due to these stochastic effects disadvantageous
mutants have a small, yet non-zero probability to reach fixation in a finite
population.

>>>>

Traditional approaches of evolutionary game theory assume that individuals meet
each other at random in an infinitely large well-mixed population; an example of
such an approach is the replicator dynamics. The replicator dynamics describes
how the abundance of strategic types in a population changes based on their
fitness. In this deterministic formulation, individuals with higher fitness
increase in abundance and ultimately, the system reaches a stable fixed point in
which the population may consist either of a single type or of a mixture of
different types. The works of~\cite{nowak2004emergence, taylor2004evolutionary,
imhof2005evolutionary, imhof2006evolutionary, traulsen2007pairwise} have shown
that constraining the population to be finite can lead to fundamental changes
due to stochastic effects. Due to these stochastic effects disadvantageous
mutants have a small, yet non-zero probability to reach fixation in a finite
population.
